---
title: "R Notebook"
output: html_notebook
---

# Week 6 weekend homework - Hypothesis testing

## Part 1
1)
```{r}
library(tidyverse)
library(janitor)
library(infer)

msleep <- ggplot2::msleep
```
2) 
H0: The mean sleep_total for all animals in the dataset differs from the mean sleep time for Jabberwockies (7 hours)
    mean_sleep_total != 7 hours
    
Ha: The mean sleep_total for all animals in the dataset is the same as the mean sleep time for Jabberwockies (7 hours)
    mean_sleep_total = 7 hours

significance level: 0.05

```{r}
observed_stat_all <- msleep %>% 
  summarise(mean_sleep_total = mean(sleep_total))

observed_stat_all
```
mean time spent sleeping is 10.43

```{r}
null_dist_all <- msleep %>% 
  specify(response = sleep_total) %>%
  hypothesise(null = "point", mu = 10.43) %>% 
  generate(reps = 5000, type = "bootstrap") %>% 
  calculate(stat = "mean") 
```

```{r}
null_dist_all %>% 
  visualise(bins = 30) +
  shade_p_value(obs_stat = observed_stat_all$mean_sleep_total,
                direction = "both")
```

```{r}
null_dist_all %>% 
  get_p_value(obs_stat = observed_stat_all$mean_sleep_total,
                direction = "both")
```
Our p-value is 0.99, meaning that the average sleep time of all animals differs from the average sleep time of Jabberwockies 99% of the time. As this is higher than our significance level of 0.05, we cannot reject our null hypothesis.

2) 
H0: On average, omnivores and herbivores sleep for similar lengths of time
    mean_sleep_total_omni = mean_sleep_total_herbi
    
Ha: On average, omnivores sleep significantly longer than herbivores
    mean_sleep_total_omni > mean_sleep_total_herbi
    
significance level: 0.05

```{r}
observed_stat_omni <- msleep %>% 
  filter(vore == "carni" | vore == "herbi") %>% 
  group_by(vore) %>% 
  summarise(mean_sleep_total = mean(sleep_total))

observed_stat_omni
```
observed average sleep for carnivores: 10.38 hrs
observed average sleep for herbivores: 9.51 hrs

```{r}
null_dist_omni <- msleep %>% 
  filter(vore == "carni" | vore == "herbi") %>% 
  group_by(vore) %>% 
  specify(response = sleep_total) %>%
  hypothesise(null = "point", mu = 9.51) %>% 
  generate(reps = 5000, type = "bootstrap") %>% 
  calculate(stat = "mean")
```

```{r}
null_dist_omni %>% 
  visualise() +
  shade_p_value(obs_stat = observed_stat_omni$mean_sleep_total,
                direction = "greater")
```

```{r}
p_value_omni <- null_dist_omni %>% 
  get_p_value(obs_stat = observed_stat_omni$mean_sleep_total,
              direction = "greater")
```
Our P-value is 0.29, meaning it is likely to observe a higher average sleep time for Carnivores than Herbivores. Therefore, we cannot reject our null hypothesis.

3)


## Part 2

1) Proportional one sample test using the draw method for the null distribution.

H0: 40% of the town population know of the coffee shop
    prop_pop = 0.4
    
Ha: More than 40% of the town population know of the coffee shop
    prop_pop > 0.4

2) Proportional paired 2 sample test using draw method for the null distribution

H0: More users click through when the banner is in the original position
    prop_group_a_CTR > prop_group_b_CTR
    
Ha: More users click through when the banner is in the new position
    prop_group_a_CTR < prop_group_b_CTR
    
3) Mean one sample test using bootstrap method for the null distribution

H0: The mean width of the part is 145mm and thus meets company standards
    mean_width = 145mm
    
Ha: The mean width of the part is not 145mm and therefore does not meet company standards
    mean_width != 145mm

## Part 3

1) Our p-value is 0.07, meaning the event of more than 40% of our sample knowing of the coffee shop is likely to happen about 7% of the time. As this is higher than our significance level of 5%, this is not seen to be a significant event and thus we cannot reject our null hypothesis that only 40% of the town knows about the coffee shop.

2) Our p-value is 0.006, meaning the event of the CTR being higher for group B (the group with the new banner position) happens only 0.6% of the time. As this is higher of our significance level of 0.01, we can reject our null hypothesis and confirm that the new banner placement leads to a higher CTR of website users.

3) Our p-value is 0.55, meaning the event of the mean part width not being equal to 145mm happens 55% of the time. This is much higher than our significance level of 0.05, meaning we cannot reject our null hypothesis that the part width meets the company standard of 145mm.





