---
title: "Week 01 weekend homework"
output: html_notebook
---

```{r}
books <- read.csv("C:/Users/kasha/Documents/CodeClan/de19_classnotes/week_01/day_5/2_weekend_homework/data/books.csv")

library(tidyverse)
```

```{r}
# Getting an idea of what the data looks like
glimpse(books)
```

```{r}
# Here we remove unneccesary cols, clean up a col name, and simplify some data
books_clean <- books %>% 
  select(rowid, title, authors, average_rating, isbn, language_code, num_pages,
         ratings_count, text_reviews_count, publication_date, publisher) %>% 
  rename(row_id = rowid) %>% 
  mutate(language_code = recode(language_code, "en-US" = "eng", .default = language_code))
books_clean
```
```{r}
#now to deal with NA's
books_clean %>% 
  summarise(across(
    everything(),
    ~sum(is.na(.x))
  ))
# There's none! :)
```
What do we want to find out about the data set?

1. Which author is the most successful?
2. Which publishing company is the most successful?
3. which book is most "talked about"?
4. What proportion of books are in english?
5. What are the longest and shortest books?

## 1. Which author is most successful - highest average rating

To find the author(s) with the highest average rating, we can group the books together by author, and take the average of their average ratings. However, books that have a low number of ratings may have an unfair advantage/disadvantage as one rating will hold more weight in the average. Therefore, we must filter out books with a relatively low number of ratings.
```{r}
books_avg <- books_clean %>% 
  filter(ratings_count > 100) %>% 
  group_by(authors) %>% 
  summarise(avg_avg_rating = mean(average_rating)) %>% 
  arrange(desc(avg_avg_rating))

books_avg 
```
Now we know that American Photographer Saul Leiter has the most popular work!

## 2. Which publisher is most successful? Highest average rating 

Similarly, we can find which publishing company has printed the most successful books on average.

```{r}
publisher_avg <- books_clean %>% 
  filter(ratings_count > 100) %>% 
  group_by(publisher) %>% 
  summarise(avg_avg_rating = mean(average_rating)) %>% 
  arrange(desc(avg_avg_rating))

publisher_avg 
```
It seems German publishing house Steidl have a keen eye for good books!

## 3. Which book is most "talked about"? Highest number of text reviews

We can find this by arranging our data by text review count.

```{r}
books_clean %>% 
  arrange(desc(text_reviews_count)) %>% 
  head(1)
```
Are we surprised? Twilight is so bad it's good!

## 4. What proportion of books are in english?

by filtering for rows where the language code = eng (english), we can divide the number of rows where this occurs by the total number of rows in our dataset to find the proportion of books in english
```{r}
books_clean %>% 
  filter(language_code == "eng") %>% 
  summarise(prop_eng = n()/nrow(books_clean))
```
almost 93% are originally written in english.

## 5. What are the longest and shortest books?

Again we can use the arrange function on the page count to find the longest and shortest books in the dataset.

```{r}
books_clean %>% 
  arrange(desc(num_pages)) %>% 
  head(1)
```
```{r}
books_clean %>% 
  arrange(desc(num_pages)) %>% 
  tail(1)
```
Both our results here take the crown for longest and shortest books on a technicality; The longest book being a collection of novels, and the shortest being an audiobook. Sneaky!











