---
title: "W05D2 homework"
output: html_notebook
---

```{r}
library(tidyverse)
library(CodeClanData)

backpack
```

```{r}
glimpse(backpack)
```

Question 2)
```{r}
ggplot(backpack) +
  aes(x = backpack_weight) +
  geom_histogram(colour = "white", fill = "orchid4") +
  labs(title = "Distribution of backpack weight amongst students",
       x = "backpack weight (lbs)")
```
The distribution shows that most students have a backpack weight of 11 lbs, followed by 5 and 8 lbs.

Question 3)

```{r}
ggplot(backpack) +
  aes(x = backpack_weight, group = sex, fill = sex) +
  geom_histogram(colour = "white", position = "dodge") +
  labs(title = "Distribution of backpack weight amongst students, varying by sex",
       x = "backpack weight (lbs)")
```
The distribution shows that girls tend to carry lighter bags than boys

Question 4)
```{r}
ggplot(backpack) +
  aes(x = body_weight, y = backpack_weight) +
  geom_point(colour = "orchid4") +
  labs(title = "Backpack Weight as a function of Body Weight",
       x = "body weight (lbs)",
       y = "backpack weight (lbs)") +
  geom_smooth(method = lm, se = FALSE, colour = "pink")
```
There is a small correlation between body weight and backpack weight

Question 5)

```{r}
ggplot(backpack) +
  aes(x = body_weight, y = backpack_weight, group = sex, colour = sex) +
  geom_point() +
  labs(title = "Backpack Weight as a function of Body Weight, By Gender",
       x = "body weight (lbs)",
       y = "backpack weight (lbs)") +
  geom_smooth(method = lm, se = FALSE)
```
There is a stronger correlation for girls than for boys.

Question 6)

```{r}
backpack_corrected <- backpack %>% 
  filter(year != 0) %>% 
  mutate(back_problems = case_when(
    back_problems == 1 ~ "yes",
    back_problems == 0 ~ "no"
  ))

backpack_corrected
```

```{r}
ggplot(backpack_corrected) +
  aes(x = back_problems) +
  geom_bar(position = "stack", fill = "orchid4") +
  labs(title = "Number of students who experience back pain vs those who don't",
       x = "Back problems")
```
Roughly 30% of students report back problems.

Question 7)

```{r}
ggplot(backpack_corrected) +
  aes(x = back_problems, group = sex) +
  geom_bar() +
  labs(title = "Number of students who experience back pain vs those who don't",
       x = "Back problems")
```

Question 8)

```{r}
ggplot(backpack_corrected) +
  aes(x = body_weight, y = backpack_weight, group = sex, colour = sex) +
  geom_point() +
  labs(title = "Backpack Weight as a function of Body Weight, by gender and reported back pain",
       x = "body weight (lbs)",
       y = "backpack weight (lbs)") +
  geom_smooth(method = lm, se = FALSE) +
  facet_wrap(~ back_problems)
```
For those without back pain, their backpack weight positively correlates with their body weight. However for men with back pain, their backpack weight decreases with their body weight.

Extension 1)

```{r}
ggplot(backpack_corrected) +
  aes(x = back_problems, group = year) +
  geom_bar()
```




